### 2012-09-24 paper_sean/introduction.tex

% !TEX root =main.tex
Robots that can move around on legs can operate in a much wider range of environments than their wheeled counterparts. A downside is that designing gaits for legged robots is a difficult and time-consuming process for human engineers~\cite{ridder storm, wetter green}, and must be repeated every time the design of a robot is changed or a new robot is created~\cite{hornby1}. 
Because of these difficulties in hand-designing gaits, scientists have investigated automatically producing gaits with machine learning or evolutionary algorithms, an approach that often produces better gaits than those created by human engineers~\cite{valsalam:mii,kohl:stone,hornby1,hornby2,yos:clune}. Both machine-created and human-created gaits perform better if they are \emph{regular}, in that they have coordinated movements, such as left-right symmetry or front-back symmetry~\cite{valsalam:mii,clune2,clune1,clune3}.
However, in most previous works, the experimenter has had to manually decide the regularities of the evolved gaits \cite{valsalam:mii,tellez,beer,raibert} . 
Such manual intervention is time consuming, requires expert knowledge, and adds constraints that may hurt performance.

@@

%The results supports previous work that evolving with a simulator and then transferring to reality is a more powerful means of achieving results than evolving directly in hardware. %JMC: Can you add a few cites here, hopefully from our current cite list? I think some of the JBM papers show this. 
%Our work also confirms that generative encodings such as HyperNEAT are a powerful way to evolve gaits and, more generally, automatically exploit regularities in challenging engineering domains.

>>>>

% !TEX root =main.tex
Robots that can move around on legs can operate in a much wider range of environments than their wheeled counterparts. A downside is that designing gaits for legged robots is a difficult and time-consuming process for human engineers~\cite{strom1999legged,wettergreen1992gait}, and must be repeated every time the design of a robot is changed or a new robot is created~\cite{hornby1}. 
Because of these difficulties in hand-designing gaits, scientists have investigated automatically producing gaits with machine learning or evolutionary algorithms, an approach that often produces better gaits than those created by human engineers~\cite{valsalam:mii,kohl:stone,hornby1,hornby2,yos:clune}. Both machine-created and human-created gaits perform better if they are \emph{regular}, in that they have coordinated movements, such as left-right symmetry or front-back symmetry~\cite{valsalam:mii,clune2,clune1,clune3}.
However, in most previous works, the experimenter has had to manually decide the regularities of the evolved gaits \cite{valsalam:mii,tellez,beer,raibert} . 
Such manual intervention is time consuming, requires expert knowledge, and adds constraints that may hurt performance.

@@

%The results supports previous work that evolving with a simulator and then transferring to reality is a more powerful means of achieving results than evolving directly in hardware. %JMC: Can you add a few cites here, hopefully from our current cite list? I think some of the JBM papers show this. %JMC: Right now I have this commented out. No need to add the cites if we leave it commented out.

%Our work also confirms that generative encodings such as HyperNEAT are a powerful way to evolve gaits and, more generally, automatically exploit regularities in challenging engineering domains.
